---
title: "Geospatial Stats "
subtitle: "TEST"
author: "Colin Havey (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

Slides: [slides.html](slides.html){target="_blank"} ( Go to `slides.qmd`
to edit)

## Introduction

Convolutional neural networks (CNNs) have become the standard approach
for automated land cover classification from satellite imagery, with
reported accuracies exceeding 90% on large benchmark datasets such as
BigEarthNet, a 480,000-patch multi-label archive covering ten European
countries (Sumbul et al., 2019). Despite this performance, CNN classifiers
typically output only a single point prediction with an associated
confidence score, and this score is not a statistically reliable estimate
of predictive uncertainty. Deep networks are frequently overconfident,
particularly for underrepresented classes. In BigEarthNet, class frequency
ranges from over 188,000 instances for "Arable land" to 1,316 for "Beaches,
dunes, sands," a roughly 140-fold imbalance that is likely to affect
classification reliability unevenly across classes.

This lack of formal uncertainty quantification has practical consequences:
point predictions provide no mechanism for distinguishing reliable
classifications from unreliable ones, which limits their use in applications
where classification errors carry meaningful cost. A recent survey of deep
learning in remote sensing identifies uncertainty quantification as a
comparatively underdeveloped area of the field, noting that most published
models report point predictions without accompanying reliability measures
(Rao et al., 2026).

This project addresses that gap by applying conformal prediction, a
distribution-free statistical framework that constructs prediction sets
with a guaranteed coverage probability, to a CNN trained on the BigEarthNet
multi-label land cover classification task. The objective is to evaluate
not only classification accuracy but also the calibration and class-wise
behavior of the resulting prediction sets, with particular attention to
whether prediction set size varies systematically with class imbalance.
The remainder of this paper reviews related work in CNN-based remote sensing
classification and conformal prediction, describes the model architecture
and calibration procedure, and presents classification and uncertainty
quantification results.

Example of writing including citing references:

*This is an introduction to ..... regression, which is a non-parametric
estimator that estimates the conditional expectation of two variables
which is random. The goal of a kernel regression is to discover the
non-linear relationship between two random variables. To discover the
non-linear relationship, kernel estimator or kernel smoothing is the
main method to estimate the curve for non-parametric statistics. In
kernel estimator, weight function is known as kernel function
[@efr2008]. Cite this paper [@bro2014principal]. The GEE [@wang2014].
The PCA [@daffertshofer2004pca]*. Topology can be used in machine 
learning [@adams2021topology]

For Symbolic Regression [@wang2019symbolic] *This is my work and I want
to add more work...*

Cite new paper [@su2012linear]

Classification of Knee OA was studied here [@guida2021knee]. This is another example of LCA [@weller2020latent]

## Methods

-   Detail the models or algorithms used.

-   Justify your choices based on the problem and data.

*The common non-parametric regression model is*
$Y_i = m(X_i) + \varepsilon_i$*, where* $Y_i$ *can be defined as the sum
of the regression function value* $m(x)$ *for* $X_i$*. Here* $m(x)$ *is
unknown and* $\varepsilon_i$ *some errors. With the help of this
definition, we can create the estimation for local averaging i.e.*
$m(x)$ *can be estimated with the product of* $Y_i$ *average and* $X_i$
*is near to* $x$*. In other words, this means that we are discovering
the line through the data points with the help of surrounding data
points. The estimation formula is printed below [@R-base]:*

$$
M_n(x) = \sum_{i=1}^{n} W_n (X_i) Y_i  \tag{1}
$$$W_n(x)$ *is the sum of weights that belongs to all real numbers.
Weights are positive numbers and small if* $X_i$ *is far from* $x$*.*

*Another equation:*

$$
y_i = \beta_0 + \beta_1 X_1 +\varepsilon_i
$$

## Analysis and Results

### Data Exploration and Visualization

-   Describe your data sources and collection process.

-   Present initial findings and insights through visualizations.

-   Highlight unexpected patterns or anomalies.

A study was conducted to determine how...

```{r, warning=FALSE, echo=T, message=FALSE}
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
```

```{python}
import pandas as pd
```

```{r, warning=FALSE, echo=TRUE}
# Load Data
kable(head(murders))

ggplot1 = murders %>% ggplot(mapping = aes(x=population/10^6, y=total)) 

  ggplot1 + geom_point(aes(col=region), size = 4) +
  geom_text_repel(aes(label=abb)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(formula = "y~x", method=lm,se = F)+
  xlab("Populations in millions (log10 scale)") + 
  ylab("Total number of murders (log10 scale)") +
  ggtitle("US Gun Murders in 2010") +
  scale_color_discrete(name = "Region")+
      theme_bw()
  

```

### Modeling and Results

-   Explain your data preprocessing and cleaning steps.

-   Present your key findings in a clear and concise manner.

-   Use visuals to support your claims.

-   **Tell a story about what the data reveals.**

```{r}

```

### Conclusion

-   Summarize your key findings.

-   Discuss the implications of your results.

## References
